Learning Discrete Bayesian Networks from Continuous Data

### 2017-05-12 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
modify the sentence

Some discretization edges appear in all three discretization methods, such as \num{1.42} and \num{2.35} for variable $C$ and \num{0.785} for variable $L$. MDL can find some important discretization edges, but it is not sensitive to find more edges.

>>>>

Some discretization edges appear in both discretization methods, such as \num{1.42} and \num{2.35} for variable $C$ and \num{0.785} for variable $L$. MDL can find some important discretization edges, but it is not sensitive to find more edges. Actually, as shown later in Section \ref{subsec:discuss_exp}, while the MDL and Bayesian methods both produce the optimal discretization as the training data grows, the Bayesian method can produce these discretizations with fewer data samples.
